---
title: "DataScience_HW3"
output: github_document
date: "2024-10-10"
---

```{r setup, include=FALSE}
library(p8105.datasets)
library(tidyverse)
library(dplyr)
data("ny_noaa")
```

Size of dataset before data cleaning: 7 variables (columns) and 2595176 observations (rows). 

Variable names include: id, date, prcp, snow, snwd, tmax, tmin. 

There is a significant amount of missing data 

```{r}
filter(ny_noaa, (is.na(snow) | snow == "") &
         (is.na(tmin) | tmin == "") &
         (is.na(tmax) | tmax == "") &
         (is.na(prcp) | prcp == "")) %>% 
  nrow()
```
There are 73950 rows that have missing data in all four columns tmax, tmin, prcp, and snow. 

```{r}
filter(ny_noaa, (is.na(tmin) | tmin == "") &
         (is.na(tmax) | tmax == "")) %>% 
  nrow()
```
And 1132502 rows that have missing data for both coloumns tmax and tmin.

The missing data is an issue, as there is inconsistancy in the data / information. 

**Do some data cleaning. Create separate variables for year, month, and day. Ensure observations for temperature, precipitation, and snowfall are given in reasonable units. For snowfall, what are the most commonly observed values? Why?**


